EP1162 Preliminary Analysis

### 2020-03-20 analysis/prelimAnalysis.Rmd
updating figures

  # Plotting function
pbai.Plot<-function(initYear,baPeriod,data=pbai) {

  p1<-
    data.frame(data[initYear],data[baPeriod]) %>% 
    setNames(c("initialBA","PBAI")) %>% 
     # filter(PBAI>=0) %>% 
      ggplot()+
    aes(x=initialBA,y=PBAI)+
    geom_point(size=3)+
    xlab(paste(initYear," plot basal area per hectare",sep=""))+
    ylab(paste("BAI per hectare for ",baPeriod, "Period"))

@@

pbai.Plot(initYear="2009",baPeriod="2009-2019")

@@

The relationship is consistent using initial BA for earlier periods (e.g., 1994):

```{r}
pbai.Plot(initYear="1994",baPeriod="2009-2019")
```

@@

pbai.Plot(initYear="1994",baPeriod="2009-2019",data=pbai.2)

@@

@@

pbai.Plot(initYear="1994",baPeriod="1994-1997")
```

>>>>

  # Plotting function
pbai.Plot<-function(initYear,baPeriod,data=pbai,x=15,y=5) {

  # Linear model to extract coefficients and R2
  mod1<-
      data.frame(data[initYear],data[baPeriod]) %>% 
      setNames(c("initialBA","PBAI")) %>% 
      lm(PBAI~initialBA,data=.)

  text1=paste(round(broom::tidy(mod1)[1,"estimate"],3),
              " + (",
              round(broom::tidy(mod1)[2,"estimate"],3),
              "X)\n",
              "R² = ",
              round(broom::glance(mod1)[1],3),
              "\np = ",
              round(broom::glance(mod1)["p.value"],3),
              sep="")

  p1<-
    data.frame(data[initYear],data[baPeriod]) %>% 
    setNames(c("initialBA","PBAI")) %>% 
     # filter(PBAI>=0) %>% 
      ggplot()+
    aes(x=initialBA,y=PBAI)+
    geom_point(size=3)+
    geom_text(label=text1,x=x,y=y,check_overlap=TRUE,hjust=0)+
    geom_smooth(method="lm",se=FALSE)+ # add regression line
    xlab(paste(initYear," plot basal area per hectare",sep=""))+
    ylab(paste("BAI per hectare for ",baPeriod, "Period"))

@@

# iteratively adjust x and y to line up text properly
pbai.Plot(initYear="2009",baPeriod="2009-2019",x=10,y=2)

@@

@@

pbai.Plot(initYear="1994",baPeriod="2009-2019",data=pbai.2,x=5,y=3)

@@

1994 period:

@@

pbai.Plot(initYear="1994",baPeriod="1994-1997",y=3.5,x=25)
```

1997 period:

pbai.Plot(initYear="1997",baPeriod="1997-2009",x=5,y=1)
```
